---
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(dplyr)
library(kableExtra)
```

```{r include=FALSE}
# Load the variables from the file
my_loaded_variables <- readRDS(paste0(getwd(), "/selected_elements.rds"))
```

```{=html}
<style type="text/css">
  .figure {
    float: right;
    text-align: center;
  }
</style>
```

```{r pressure, echo=FALSE, fig.align = "right", out.width = '30%', out.extra='style="float: right; margin-right: 10px; margin-top: 20px"'}
knitr::include_graphics(paste0(getwd(),"/PhyloTrace_bw.png"))
```

# cgMLST Report

`r if(my_loaded_variables[["report_df.Include"]][2]) {if(my_loaded_variables[["report_df.Include"]][3]) {my_loaded_variables[["general_date"]]}} `

`r if(my_loaded_variables[["report_df.Include"]][2]) {if(my_loaded_variables[["report_df.Include"]][4]) {my_loaded_variables[["operator"]]}} `

`r if(my_loaded_variables[["report_df.Include"]][2]) {if(my_loaded_variables[["report_df.Include"]][5]) {my_loaded_variables[["institute"]]}} `

***

`r if(my_loaded_variables[["report_df.Include"]][2]) {if(my_loaded_variables[["report_df.Include"]][6]) {my_loaded_variables[["comment"]]}} `

\

```{r echo=FALSE, fig.align = "center", out.width='100%'}
if(!my_loaded_variables[["plot"]] == "MST"){
  if(my_loaded_variables[["report_df.Include"]][13]) {
  knitr::include_graphics(paste0(my_loaded_variables[["plot"]], ".jpeg"))
  }
} else {
  if(my_loaded_variables[["report_df.Include"]][13]) {
  knitr::include_graphics(paste0(my_loaded_variables[["plot"]], ".jpg"))
  }
}
```

\

```{r echo=FALSE}
if(my_loaded_variables[["report_df.Include"]][1]) {
  kable(select(my_loaded_variables[["entry_table"]], my_loaded_variables[["table_columns"]]), 
      row.names = FALSE,
      linesep = "") %>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE, font_size = 10) %>%
  row_spec(1:nrow(my_loaded_variables[["entry_table"]]),
           extra_css = "padding: 3px")
}
```

\

```{r echo=FALSE}
if(!is.null(my_loaded_variables[["na_handling"]])){
  if(my_loaded_variables[["na_handling"]] == "ignore_na") {
    my_loaded_variables[["na_handling"]] <- "Ignore missing values for pairwise comparison"
  } else if (my_loaded_variables[["na_handling"]] == "omit") {
    my_loaded_variables[["na_handling"]] <- "Omit loci with missing values for all assemblies"
  } else  {
    my_loaded_variables[["na_handling"]] <- "Treat missing values as allele variant"
  }
} 

if(my_loaded_variables[["report_df.Include"]][7] == TRUE) {
  show_analysis <- TRUE
} else {
  show_analysis <- FALSE
}
 
if(!is.null(my_loaded_variables[["na_handling"]])){
  df <- data.frame(Item = c(if(my_loaded_variables[["report_df.Include"]][9]){"Tree construction"},
                          if(my_loaded_variables[["report_df.Include"]][10]){"Distance algorithm"},
                          if(my_loaded_variables[["report_df.Include"]][11]){"Missing value handling"},
                          if(my_loaded_variables[["report_df.Include"]][12]){"PhyloTrace version"},
                          if(my_loaded_variables[["report_df.Include"]][12]){"pblat version"}),
                 Content = c(if(my_loaded_variables[["report_df.Include"]][9]){my_loaded_variables[["tree"]]},
                             if(my_loaded_variables[["report_df.Include"]][10]){my_loaded_variables[["distance"]]},
                             if(my_loaded_variables[["report_df.Include"]][11]){my_loaded_variables[["na_handling"]]},
                             if(my_loaded_variables[["report_df.Include"]][12]){my_loaded_variables[["version"]][1]},
                             if(my_loaded_variables[["report_df.Include"]][12]){my_loaded_variables[["version"]][2]})
                           )
} else {
  df <- data.frame(Item = c(if(my_loaded_variables[["report_df.Include"]][9]){"Tree construction"},
                          if(my_loaded_variables[["report_df.Include"]][10]){"Distance algorithm"},
                          if(my_loaded_variables[["report_df.Include"]][12]){"PhyloTrace version"},
                          if(my_loaded_variables[["report_df.Include"]][12]){"pblat version"}),
                 Content = c(if(my_loaded_variables[["report_df.Include"]][9]){my_loaded_variables[["tree"]]},
                             if(my_loaded_variables[["report_df.Include"]][10]){my_loaded_variables[["distance"]]},
                             if(my_loaded_variables[["report_df.Include"]][12]){my_loaded_variables[["version"]][1]},
                             if(my_loaded_variables[["report_df.Include"]][12]){my_loaded_variables[["version"]][2]})
                           )
}
colnames(df) <- NULL

if(my_loaded_variables[["report_df.Include"]][7] & show_analysis){
  kbl(df) %>%
  kable_styling(position = "float_left",
                font_size = 10) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "15em", background = "#F9F9F9")%>%
  pack_rows("Analysis parameter", 1, nrow(df), 
            bold = FALSE,
            label_row_css = "font-size: 20px; padding: 19px",
            hline_before = F,
            hline_after = F)
}
if(my_loaded_variables[["report_df.Include"]][8] & show_analysis) {
  kbl(my_loaded_variables[["scheme"]]) %>%
  kable_styling(position = "right",
                font_size = 10) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "45em", background = "#F9F9F9") %>%
  pack_rows("cgMLST Scheme", 1, nrow(my_loaded_variables[["scheme"]]), 
            bold = FALSE,
            label_row_css = "font-size: 20px; padding: 19px",
            hline_before = FALSE,
            hline_after = F)
}

```
